Is It Possible to Steal Money Through USB-C?

### 2020-12-21 WOOT/Files/badusb.tex
Add Latex utility

\subsection{Implementation}
The implementation of \tool extends several existing offensive BadUSB device including Rubber Ducky\hongyi{Add Citation} (where we implement the co-operation of HID emulation and screen streaming) and Raspberry Pi (on which we implement the capture of video stream and its processing). We implemented the QR-Code extraction agent from scratch. The complete workflow of \tool, demonstrating the interaction of all the components is presented at Fig.~\ref{fig:workflow}.

>>>>

\subsection{Implementation}
The implementation of \tool\ extends several existing offensive BadUSB device including Rubber Ducky\hongyi{Add Citation} (where we implement the co-operation of HID emulation and screen streaming) and Raspberry Pi (on which we implement the capture of video stream and its processing). We implemented the QR-Code extraction agent from scratch. The complete workflow of \tool, demonstrating the interaction of all the components is presented at Fig.~\ref{fig:workflow}.
